Automating Verification of MPC Security

### 2023-06-15 popl24/minicat.tex
checkpoint

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X = \{ \store_X | \store \in \stores \}$.

>>>>

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X \defeq \{ \store_X | \store \in \stores \}$.

### 2023-06-15 popl24/pmf.tex
checkpoint

\begin{definition}
  Given $\pdf{X}$, its \emph{conditional distribution given
  $\stores$} with $\dom(\stores) = Y$ and $Y \subseteq X$, denoted
  $\condd{\pdf{X}}{\stores}$, is a distribution with domain $X$ where for all
  $\store \in \mems(X)$:
  $$
  (\condd{\pdf{X}}{\stores})(\store) =
  (\sum_{\store' \in \stores} \pdf{X}(\store \cap \store')) /
  (\sum_{\store' \in \stores} \pdf{X}(\store'))
  $$
  where $\pdf{X}(\store \cap \store')) = 0$ if $\store \cap \store'$ is undefined.
  we write $\condd{\pdf{X}}{\store}$ as an abbreviation for $\condd{\pdf{X}}{\{ \store \}}$.
\end{definition}
To recover familiar notation we allow the following syntactic
sugarings:
\begin{eqnarray*}
\pdf{X}(\store|\store') &\defeq& (\condd{\pdf{X}}{\store})(\store')\\
\pdf{X}(\store) &\defeq& (\margd{\pdf{X}}{\dom(\store)})(\store) \qquad \dom(\store) \subset X
\end{eqnarray*}

>>>>

\begin{definition}
  Given $\pdf{X}$, its \emph{conditional distribution given
  $\stores$} with $\dom(\stores) = Y$ with $Y \subseteq X$, denoted
  $\condd{\pdf{X}}{\stores}$, is a distribution with domain $X$ where for all
  $\store \in \mems(X)$:
  $$
  (\condd{\pdf{X}}{\stores})(\store) =
  (\sum_{\store' \in \stores} \pdf{X}(\store \cap \store')) /
  (\sum_{\store' \in \stores} (\margd{\pdf{X}}{Y})(\store'))
  $$
  where $\pdf{X}(\store \cap \store')) = 0$ if $\store \cap \store'$ is undefined.
  we write $\condd{\pdf{X}}{\store}$ as an abbreviation for $\condd{\pdf{X}}{\{ \store \}}$.
\end{definition}
To recover familiar notation we allow the following syntactic
sugarings:
\begin{eqnarray*}
\pdf{X}(\store|\store') &\defeq& (\condd{\pdf{X}}{\store})(\store')\\
\pdf{X}(\store) &\defeq& (\margd{\pdf{X}}{\dom(\store)})(\store) \qquad \dom(\store) \subset X
\end{eqnarray*}
